Legends for Figures

### 2019-01-20 Manuscript/Figures/figure_legends.Rmd
Fig 1 legend done

# Figure 1: Model Construction

Diagram of the model construction used for downstream analysis. The linear genome was binned according to the resolution of the respective HiC experiment (either 5kb, 25kb, 50kb, or 100kb intervals). TAD boundaries were then flanked by 1-unit on either side of the boundary point. The unit flanking was indicative of the resolution that the domain data was obtained from (i.e. for 5kb resolution, 1 unit represents 5kb for a total flanking region of 10kb). The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region. The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.

>>>>

**Figure 1: Model Construction.** The linear genome was binned according to the resolution of the Hi-C data. TAD boundaries were then flanked by 1 resolution-unit on both sides of the boundary point. [??? The following is unclear. Show Y on the figure. Are you talking about overlap only?] The response vector Y used for classification was determined by whether or not a genomic bin overlapped with a flanked region. The positional coordinates of each functional genomic element, obtained from ENCODE, were then used to define the feature space of the models.
